Viral Sequence Sorting Tools - Rules on Fragments

### 2023-04-01 TestingPipeline/Scripts/visualizing_rules_on_short_fragments.Rmd
Updating figures with current rules.
Updating figures.

## Calculate the performance of each pipeline
```{r}
accuracy_scores <- data.frame(testing_set_index=rep(0, nrow(combos_list)*10),
                      precision=rep(0, nrow(combos_list)*10),
                       recall=rep(0, nrow(combos_list)*10),
                       F1=rep(0, nrow(combos_list)*10),
                       MCC=rep(0, nrow(combos_list)*10), 
                      AUC=rep(0, nrow(combos_list)*10))

accuracy_scores <- cbind(testing_set_index=rep(1, nrow(combos_list)),
                              build_score_list(viruses[viruses$Index==1,], combos_list))
for (i in 2:10) {
  accuracy_scores <- rbind(accuracy_scores,
                           cbind(testing_set_index=rep(i, nrow(combos_list)),
                              build_score_list(viruses[viruses$Index==i,], combos_list)))
}
```

@@

```{r}
ggplot(accuracy_scores_melt[accuracy_scores_melt$performance_metric!="MCC",], aes(x=numrules, y=performance_metric_score, 
                                  color=numrules, fill=numrules)) +
  geom_boxplot() +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  ylab("Score") +
  xlab("Number of Rule Sets") +
  scale_fill_manual(name="",
                     values = alpha(rev(pal(6)), 0.5)) +
  scale_color_manual(name="",
                     values = alpha(rev(pal(6)), 1)) +
  facet_wrap(~performance_metric)

@@

```{r}
one.way <- aov(MCC ~ numrules, data = accuracy_scores)

>>>>

## Calculate the performance of each pipeline
```{r}
accuracy_scores <- data.frame(testing_set_index=rep(0, nrow(combos_list)*5),
                      precision=rep(0, nrow(combos_list)*5),
                       recall=rep(0, nrow(combos_list)*5),
                       F1=rep(0, nrow(combos_list)*5),
                       MCC=rep(0, nrow(combos_list)*5), 
                      AUC=rep(0, nrow(combos_list)*5))

accuracy_scores <- cbind(testing_set_index=rep(1, nrow(combos_list)),
                              build_score_list(viruses[viruses$Index==1,], combos_list))
for (i in 2:5) {
  accuracy_scores <- rbind(accuracy_scores,
                           cbind(testing_set_index=rep(i, nrow(combos_list)),
                              build_score_list(viruses[viruses$Index==i,], combos_list)))
}
```

@@

```{r}
accuracy_scores$numrules <- as.factor(accuracy_scores$numrules)

accuracy_scores_melt <- accuracy_scores %>% 
  select(testing_set_index, precision, recall, MCC, numrules, toolcombo) %>%
  pivot_longer(cols=c(precision, recall, MCC), 
               names_to="performance_metric",
               values_to="performance_metric_score")
```

```{r}
ggplot(accuracy_scores_melt[accuracy_scores_melt$performance_metric!="MCC",], aes(x=numrules, y=performance_metric_score, 
                                  color=numrules, fill=numrules)) +
  geom_boxplot() +
  geom_point(alpha=0.5) +
  theme_light() +
  theme(
    panel.grid.major.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = "bottom",
    axis.text.y=element_text(size=14),
    axis.text.x=element_text(size=14, angle = 90),
    legend.text=element_text(size=12),
    axis.title=element_text(size=16),
  ) +
  ylab("Score") +
  xlab("Number of Rule Sets") +
  scale_fill_manual(name="Number of Rule Sets",
                     values = alpha(rev(viridis(6)), 0.5)) +
  scale_color_manual(name="Number of Rule Sets",
                     values = alpha(rev(viridis(6)), 1)) +
  facet_wrap(~performance_metric)

@@

```{r}
accuracy_scores$numrules <- as.factor(accuracy_scores$numrules)
one.way <- aov(MCC ~ numrules, data = accuracy_scores)
